### 2023-09-19 3.Design/inverter.tex
worked on area
upgraded inv part

\begin{figure}[H]
  \centering
  \hspace*{2.5cm}
  \subfloat[Inverter's circuit]{\label{circt:inv}\includesvg[height=3cm]{inverter/invCircuit}}%
  \hfill
  \subfloat[Inverter's symbol]{\label{fig:invSymbol}\includesvg[height=2.5cm]{inverter/invSymbol}}%
  \hspace*{1.5cm}
  \caption{}
  \label{fig:inv}
\end{figure}

\Cref{fig:inv} combines the circuit and the symbol of the inverter used in this thesis.

@@

With $A_{CMOS}= w\cdot l$ TODO check w et l

>>>>

\begin{figure}[H]
  \centering
  \hspace*{2.5cm}
  \subfloat[Inverter's circuit]{\label{circt:inv}\includesvg[height=3cm]{inverter/invCircuit}}%
  \hfill
  \subfloat[Inverter's symbol]{\label{sym:inv}\includesvg[height=2.5cm]{inverter/invSymbol}}%
  \hspace*{1.5cm}
  \caption{}
  \label{fig:inv}
\end{figure}

Like mentionned, the circuit for the inverter is very straight forward (\cref{circt:inv}). The symbol is nothing fancy as well as it is the classic symbol (\cref{sym:inv}) for such a circuit.

@@

With $A_{CMOS}= w\cdot l=2\cdot 10^{-7}\cdot6\cdot10^{-8} =1.2\cdot10^{-14}m^2$
